---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "figs/"
)
```

## violinplot

Violin plot is a method for plotting numeric data using a
rotated/mirrored kernel density plot. Other implementations exist
(namely from [ggplot2](https://github.com/hadley/ggplot2)) that
provide extensive customization. This package provides an alternative
implementation that relies solely on base graphics, yet still provides
methods for `data.frame`, `matrix`, `list`, `numeric` vectors, and `formula`.

## Installation

It's not yet submitted to CRAN, so the only option currently is to
import the development version from github:

```{r, eval = FALSE}
devtools::install_github("r2evans/violinplot")
```

## Sample Usage

```{r}
library(violinplot)
```

Anything (I think) that works for `boxplot` also works for `violinplot`:

```{r, eval = FALSE}
violinplot(mtcars$mpg, main = "Single Vector")
violinplot(mtcars$mpg, mtcars$cyl, col = 2:4,
           main = "Two Vectors")
```

And, though `boxplot` already supports a "formula" method, the
`violinplot.formula` method has been extended to provide spacing
between the groups of factors:

```{r singlefactor}
violinplot(mpg ~ cyl, data = mtcars, col = 2:4,
           main = "Single Factor Formula")
```

More complex formulas can be used as well:

```{r multifactor}
violinplot(mpg ~ cyl + vs, data = mtcars, col = 2:4,
           main = "Multi-Factor Formula")
```
